---
title: "demographics-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{cancerprof-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Load the package
```{r setup}
library(cancerprof)
```

## Retrieving Data

The demographics category of cancerprof contains 11 unique functions to pull data from the demographics page of [State Cancer Profile](https://statecancerprofiles.cancer.gov/demographics/index.php).

These functions are: `demo_crowding()`, `demo_education()`, `demo_food()`, `demo_income()`, `demo_insurance()`, `demo_mobility()`, `demo_non_english_language()`, `demo_population()`, `demo_poverty()`, `demo_svi()`, `demo_workforce()`

Each of these functions require various parameters that must be specified to pull data. Please refer to function documentation for more details.

### Demo Crowding
Demo crowding always requires 3 arguments: area, areatype, and race

```{r}
# demo_education("wa", "county", "at least high school", "males")
demo_food("wa", "county", "food insecurity", "black")
```
