---
title: "Demographics"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{cancerprof-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Load the package
```{r setup}
library(cancerprof)
```

## Retrieving Data

The demographics category of cancerprof contains 11 unique functions to pull data from the demographics page of [State Cancer Profile](https://statecancerprofiles.cancer.gov/demographics/index.php).

These functions are: `demo_crowding()`, `demo_education()`, `demo_food()`, `demo_income()`, `demo_insurance()`, `demo_mobility()`, `demo_non_english_language()`, `demo_population()`, `demo_poverty()`, `demo_svi()`, `demo_workforce()`

Each of these functions require various parameters that must be specified to pull data. Please refer to function documentation for more details.

### Demo Crowding
Demo crowding **Always** requires 4 arguments: area, areatype, crowding, and race

```{r crowding}
crowding <- demo_crowding(
  area = "WA",
  areatype = "county",
  crowding = "household with >1 person per room",
  race = "All Races (includes Hispanic)"
)
head(crowding, n = 3)
```

### Demo Education
Demo education has 5 arguments: area, areatype, education, sex, race.

**Depending on the education argument, the required arguments will change**
```{r education}
# at least high school - requires arguments: area, areatype, education, sex
education1 <- demo_education(
  area = "wa",
  areatype = "county",
  education = "at least high school",
  sex = "males"
)

head(education1, n = 3)

# at least bachelors degree - requires arguments: area, areatype, education, sex, race
education2 <- demo_education(
  area = "usa",
  areatype = "state",
  education = "at least bachelors degree",
  sex = "both sexes",
  race = "all races (includes hispanic)"
)

head(education2, n = 3)

# less than 9th grade - requires arguments: area, areatype, education
education3 <- demo_education(
  area = "pr",
  areatype = "hsa",
  education = "less than 9th grade"
)

head(education3, n = 3)
```

### Demo Food
Demo food has 4 arguments: area, areatype, food, race.

```{r food}
# limited access to healthy food - requires arguments: area, areatype, food
food1 <- demo_food(
  area = "usa",
  areatype = "state",
  food = "limited access to healthy food"
)

head(food1, n = 3)

# food insecurity - requires arguments: area, areatype, food, race
food2 <- demo_food(
  area = "pr",
  areatype = "county",
  food = "food insecurity",
  race = "all races (includes hispanic)"
)

head(food2, n = 3)
```

### Demo Income
Demo income **Always** requires 4 arguments: area, areatype, income, race.

```{r income}
# limited access to healthy food - requires arguments: area, areatype, food
income1 <- demo_income(
  area = "wa",
  areatype = "county",
  income = "median household income",
  race = "all races (includes hispanic)"
)

head(income1, n = 3)

# food insecurity - requires arguments: area, areatype, food, race
income2 <- demo_income(
  area = "usa",
  areatype = "state",
  income = "median family income",
  race = "all races (includes hispanic)"
)

head(income2, n = 3)
```

### Demo Insurance
Demo insurance has 6 arguments: area, areatype, insurance, sex, age, race.

**Please note that the age arguments for "both sexes" is different than "Males and "Females"**
Check function documentations for more details

Only Areatype "State" can select Race, otherwise race should always be "all races (includes hispanic)

```{r insurance}
insurance1 <- demo_insurance(
  area = "usa",
  areatype = "state",
  insurance = "% Insured in demographic group, all income levels",
  sex = "both sexes",
  age = "18 to 64 years",
  race = "white (non-hispanic)"
)

head(insurance1, n = 3)

insurance2 <- demo_insurance(
  area = "wa",
  areatype = "county",
  insurance = "% Insured in demographic group, all income levels",
  sex = "males",
  age = "18 to 64 years"
)

head(insurance2, n = 3)
```

### Demo Mobility
Demo mobility **Always** requires 3 arguments: area, areatype, mobility. The function defaults to "all races", "both sexes", "ages 1+"

```{r mobility}
mobility1 <- demo_mobility(
  area = "usa",
  areatype = "state",
  mobility = "moved, same county (in past year)"
)

head(mobility1, n = 3)


mobility2 <- demo_mobility(
  area = "WA",
  areatype = "county",
  mobility = "moved, different county, same state (in past year)"
)

head(mobility2, n = 3)
```

### Demo Language
Demo Language **Always** requires 3 arguments: area, areatype, language. The function defaults to "all races", "both sexes", "ages 14+"

```{r Language}
non_english1 <- demo_language(
  area = "wa",
  areatype = "county",
  language = "language isolation"
)

head(non_english1, n = 3)


non_english2 <- demo_language(
  area = "usa",
  areatype = "state",
  language = "language isolation"
)

head(non_english2, n = 3)
```

### Demo Population
Demo Population has 5 arguments: area, areatype, population, race, sex. The population argument is used to input a population variable such as age, race, or sex. Please note that this different from the race and sex arguments and different population variables will default race, sex, and age.

*If you select "foreign born" for population, you must provide another race for the race argument*

```{r population}
#
population1 <- demo_population(
  area = "wa",
  areatype = "county",
  population = "foreign born",
  race = "black",
  sex = "females"
)

head(population1, n = 3)


population2 <- demo_population(
  area = "ca",
  areatype = "county",
  population = "males",
  race = "all races (includes hispanic)"
)

head(population2, n = 3)

population3 <- demo_population(
  area = "usa",
  areatype = "state",
  population = "age under 18",
  race = "all races (includes hispanic)",
  sex = "both sexes"
)

head(population3, n = 3)
```

### Demo Poverty
Demo poverty has 5 arguments: area, areatype, poverty, race, sex. The function defaults to "all ages"

The "persistent poverty" and "persons <150% of poverty" poverty argument will default to "all races", "both sexes", "all ages". 

The "families below poverty" poverty argument will require a race argument and default to "both sexes" and "all ages". 

The "persons below poverty" poverty argument will require a race argument and a sex argument, and default to "all ages".

```{r poverty}
# Persistent poverty
poverty1 <- demo_poverty(
  area = "WA",
  areatype = "county",
  poverty = "persistent poverty"
)

head(poverty1, n = 3)

# Families below poverty
poverty2 <- demo_poverty(
  area = "usa",
  areatype = "state",
  poverty = "families below poverty",
  race = "black"
)

head(poverty2, n = 3)

# Persons below poverty
poverty3 <- demo_poverty(
  area = "usa",
  areatype = "state",
  poverty = "persons below poverty",
  race = "black",
  sex = "males"
)

head(poverty3, n = 3)
```

### Demo Social Vulnerability Index (SVI)
Demo svi **Always** requires 2 arguments: area, svi. The function defaults to "all races", "both sexes", "all ages."

*Please note that the areatype argument is not available for this function because areatype is limited to "county"*

```{r svi}
svi1 <- demo_svi(
  area = "WA",
  svi = "overall"
)

head(svi1, n = 3)


svi2 <- demo_svi(
  area = "usa",
  svi = "socioeconomic status"
)

head(svi2, n = 3)
```

### Workforce
Demo svi **Always** requires 5 arguments: area, areatype, workforce, race, sex. The function defaults to "ages 16+"

```{r workforce}
workforce1 <- demo_workforce(
  area = "WA",
  areatype = "county",
  workforce = "unemployed",
  race = "all races (includes hispanic)",
  sex = "both sexes"
)

head(workforce1, n = 3)


workforce2 <- demo_workforce(
  area = "usa",
  areatype = "state",
  workforce = "unemployed",
  race = "all races (includes hispanic)",
  sex = "females"
)

head(workforce2, n = 3)
```
