---
title: "incidence-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{incidence-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Load the package
```{r setup}
library(cancerprof)
```

## Retrieving Data

The Cancer Incidence category of cancerprof contains a single functions to pull data from the Incidence page of [State Cancer Profile](https://statecancerprofiles.cancer.gov/incidencerates/index.php).

The function for retrieving incidence data is `incidence_cancer()`

## Incidence Cancer
Incidence cancer has 23 cancer types to choose from. In total, incidence cancer has 8 arguments:
area, areatype, cancer, race, sex, age, stage, year

### Argument Details
- The `"latest single year (us by state)"` argument for year can only be selected if `area` is `"state"`

- For the following cancer types: 
    + "breast (female in situ)",
    + "childhood (ages <15, all sites)",
    + "childhood (ages <20, all sites)",
    + "leukemia"

  The `stage` argument must by `"all stages"` 

- For the following cancer types: 
    + "breast (female)",
    + "breast (female in situ)",
    + "ovary",
    + "uterus (corpus & uterus, nos)"

  The `sex` argument must by `"females"` 
  
- For `"prostate"` cancer, sex must be `"males"`
- For `"childhood (ages <15, all sites)"`, age must be `"ages <15"`
- For `"childhood (ages <20, all sites)"`, age must be `"ages <20"`

### Examples

```{r incidence}
incidence1 <- incidence_cancer(
  area = "usa",
  areatype = "state",
  cancer = "lung & bronchus",
  race = "all races (includes hispanic)",
  sex = "males",
  age = "ages 50+",
  stage = "late stage (regional & distant)",
  year = "latest single year (us by state)"
)
head(incidence1, n = 3)

incidence2 <- incidence_cancer(
  area = "wa",
  areatype = "hsa",
  cancer = "ovary",
  race = "all races (includes hispanic)",
  sex = "females",
  age = "ages 50+",
  stage = "late stage (regional & distant)",
  year = "latest 5 year average"
)
head(incidence2, n = 3)

incidence3 <- incidence_cancer(
  area = "wa",
  areatype = "county",
  cancer = "all cancer sites",
  race = "black (non-hispanic)",
  sex = "both sexes",
  age = "ages 65+",
  stage = "all stages",
  year = "latest 5 year average"
)
head(incidence3, n = 3)
```
