---
title: "mortality-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{mortality-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Load the package
```{r setup}
library(cancerprof)
```

## Retrieving Data

The Cancer Mortality category of cancerprof contains a single functions to pull data from the Mortality page of [State Cancer Profile](https://statecancerprofiles.cancer.gov/deathrates/index.php).

The function for retrieving incidence data is `mortality_cancer()`

## Mortality Cancer
Mortality cancer has 22 cancer types to choose from. In total, incidence cancer has 7 arguments:
area, areatype, cancer, race, sex, age, year

### Argument Details
- The `"latest single year (us by state)"` argument for year can only be selected if `area` is `"state"`

- For the following cancer types: 
    + "breast (female)",
    + "ovary",
    + "uterus (corpus & uterus, nos)"

  The `sex` argument must by `"females"` 
  
- For `"prostate"` cancer, sex must be `"males"`
- For `"childhood (ages <15, all sites)"`, age must be `"ages <15"`
- For `"childhood (ages <20, all sites)"`, age must be `"ages <20"`

### Examples

```{r mortality}
mortality1 <- mortality_cancer(
  area = "wa",
  areatype = "county",
  cancer = "all cancer sites",
  race = "black (non-hispanic)",
  sex = "both sexes",
  age = "ages 65+",
  year = "latest 5 year average"
)
head(mortality1, n = 3)

mortality2 <- mortality_cancer(
  area = "usa",
  areatype = "state",
  cancer = "prostate",
  race = "all races (includes hispanic)",
  sex = "males",
  age = "ages 50+",
  year = "latest single year (us by state)"
)
head(mortality2, n = 3)

mortality3 <- mortality_cancer(
  area = "wa",
  areatype = "hsa",
  cancer = "ovary",
  race = "all races (includes hispanic)",
  sex = "females",
  age = "ages 50+",
  year = "latest 5 year average"
)
head(mortality3, n = 3)
```
