---
title: "Screening and Risk Factors"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{risks-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Load the package
```{r setup}
library(cancerprof)
```

## Retrieving Data

The Screening and Risk Factors category of cancerprof contains 6 unique functions to pull data from the demographics page of [State Cancer Profile](https://statecancerprofiles.cancer.gov/demographics/index.php).

These functions are: `risk_alcohol()`, `risk_colorectal_screening()`, `risk_diet_exercise()`, `risk_smoking()`, `risk_vaccines()`, `risk_womens_health()`

Each of these functions require various parameters that must be specified to pull data. Please refer to function documentation for more details.

### Risk Alcohol
Risk Alcohol requires 3 arguments: alcohol, race, sex

```{r alcohol}
alcohol1 <- risk_alcohol(alcohol = paste("binge drinking (4+ drinks on one occasion for women,", 
                                         "5+ drinks for one occasion for men), ages 21+"), 
                         race = "all races (includes hispanic)", 
                         sex = "both sexes")
head(alcohol1, n=3)
```

### Risk Colorectal Screening
Risk Colorectal Screening has 4 arguments: screening, race, sex, area

"home blood stool test in the past year, ages 45-75" and "received at least one recommended crc test, ages 45-75" for the screening arguments requires a race argument and a sex argument and defaults to "direct estimates", "US by state".

"ever had fobt, ages 50-75", "guidance sufficient crc, ages 50-75", "had colonoscopy in past 10 years, ages 50-75" for the screening arguments defaults to "all races", "both sexes", and "county level modeled estimates"

```{r colorectal screening}
screening1 <- risk_colorectal_screening(screening = "home blood stool test in the past year, ages 45-75",
                                     race = "all races (includes hispanic)",
                                     sex = "both sexes")
head(screening1, n=3)

screening2 <- risk_colorectal_screening(screening = "ever had fobt, ages 50-75",
                                        area="usa")
head(screening2, n=3)
```








